---
title: "Marina's Scratch Script for Trialing Pipeline"
format: html
editor_options: 
  chunk_output_type: console
---

```{r}
# load libraries
library(tidyverse)
library(janitor)
library(googledrive)
library(googlesheets4)

# source functions
source("index_data_processing_functions.r")

data <- readRDS(here::here("data", "logger_data.rds"))
files <- readRDS("processed_files.rds")

# authenticate google drive
drive_auth()
```

https://drive.google.com/drive/u/0/folders/1MZxIPozLI_K6ietpjLzEM-ybJjGT-a48

```{r}
# Test function to get google files from drive
temp_files <- get_logger_csvs_by_id("1MZxIPozLI_K6ietpjLzEM-ybJjGT-a48")

# YES
```

```{r}
# Test fuction to get google files for ALL loggers
logger_files <- get_all_logger_csvs_by_id(root_folder_id)

# Gorg. 


# Grab and clean metadata
metadata <- read_and_clean_metadata(metadata_file_url, sheet_name)
```


```{r}
source("index_data_processing_functions.r")
```


```{r}
# Test cleaning function for each sensor type ----

# PAR
par_files <- logger_files |>
  filter(sensor_type == "PAR") |>
  distinct()

df_par <- purrr::map_dfr(seq_len(nrow(par_files)), function(i) {
  read_and_clean_logger_csv(par_files[i, ], metadata)
})

unique(df_par$site)
range(df_par$datetime)

# Edmonds PAR 15605 is actually PAR 3 bottom... ... But naming convention is different and throwing of the position assignment
# Also jeffersonhead PAR6424 is PAR5 bottom


df_par_na_pos <- df_par |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_par_na_pos[,c('site','par_logger_id','position')])

# WL - kpa
df_wl <- read_and_clean_logger_csv(logger_files[29, ])
View(df_wl)

# WL - psi
df_wl2 <- read_and_clean_logger_csv(logger_files[32, ])
View(df_wl2)

# WL - both
wl_files <- logger_files |>
  filter(sensor_type == "WL") |>
  distinct()

df_wl <- purrr::map_dfr(seq_len(nrow(wl_files)), function(i) {
  read_and_clean_logger_csv(wl_files[i, ], metadata)
})

unique(df_wl$site)
# are vashon and pointvashon the same site?
range(df_wl$datetime)

df_wl_na_pos <- df_wl |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_wl_na_pos[,c('site','wl_logger_id','position')])


# TEMP
df_temp <- read_and_clean_logger_csv(logger_files[296, ], metadata = metadata)

temp_files <- logger_files |>
  filter(sensor_type == "TEMP") |>
  distinct()

df_temp <- purrr::map_dfr(seq_len(nrow(temp_files)), function(i) {
  read_and_clean_logger_csv(temp_files[i, ], metadata)
})

unique(df_temp$site)
range(df_temp$datetime)

df_temp_na_pos <- df_temp |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_temp_na_pos[,c('site','temp_logger_id','position')])

library(plotly)

ggplotly(df_temp |>
           # filter(site == "jeffersonhead",
           #        position == "surface",
           #        year(datetime) == 2023) |>
           ggplot() +
           geom_point(aes(x = datetime, y = temp_c, color = temp_logger_id), size = 0.1) +
           facet_wrap(~site))

# ok so... the filtering is not perfect. because some files are kinda weirdly duplicating each other 
# but then are not mentioned in the metadata.. EX: Edmonds_T3_2024-04-03 is from 12/06/2023 12:45:00 to 06/18/2024 7:45:00
# while Edmonds_T3_2023-12-14.csv is from 12/06/2023 12:45:00 to 04/03/2024 10:15:00. 
# somehow in the metadata we will want to filter Edmonds_T3_2024-04-03 to actually start at 04/03/2023


# PH
df_ph <- read_and_clean_logger_csv(logger_files[107, ])

ph_files <- logger_files |>
  filter(sensor_type == "pH") |>
  distinct()

df_ph <- purrr::map_dfr(seq_len(nrow(ph_files)), function(i) {
  read_and_clean_logger_csv(ph_files[i, ], metadata)
})

unique(df_ph$site)
range(df_ph$datetime)

df_ph_na_pos <- df_ph |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_ph_na_pos[,c('site','ph_logger_id','position')])

# DO
df_do <- read_and_clean_logger_csv(do_files)
View(df_do)

do_files <- logger_files |>
  filter(sensor_type == "DO") |>
  distinct()

df_do <- purrr::map_dfr(seq_len(nrow(do_files)), function(i) {
  read_and_clean_logger_csv(do_files[i, ], metadata)
})

unique(df_do$site)
range(df_do$datetime)

df_do_na_pos <- df_do |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_do_na_pos[,c('site','do_logger_id','position')])

# CON
con_files <- logger_files |>
  filter(sensor_type == "CON") |>
  distinct()

df_con <- purrr::map_dfr(seq_len(nrow(con_files)), function(i) {
  read_and_clean_logger_csv(con_files[i, ], metadata)
})

# What does the star mean on some site names?
# Are vashon and point vashon the same?

unique(df_con$site)
range(df_con$datetime)

df_con_na_pos <- df_con |>
  filter(is.na(position))
# Loggers to look into where position couldn't parse:
unique(df_con_na_pos[,c('site','con_logger_id','position')])
```

```{r}
all <- df_temp |>
  full_join(df_ph, by = c("site", "datetime", "position")) |>
  full_join(df_do, by = c("site", "datetime", "position")) |>
  full_join(df_wl, by = c("site", "datetime", "position")) |>
  full_join(df_par, by = c("site", "datetime", "position")) |>
  full_join(df_con, by = c("site", "datetime", "position"))
```

This is not giving what I want because... Some of these are at the surface and some are at the bottom. so im seeing what SEEM like duplicates but... Yeah. So I need to distinguish there before I joing everything. 

I need to clean the metadata as a part of all of this. Alrighty!!!!!!!!!!!

```{r}

metadata_raw <- read_sheet("https://docs.google.com/spreadsheets/d/1JJ4Vtb_pI9FJRvMYg7pbhQzM6JPcFzGVU3rR9IdYnGQ/edit?gid=1334564098#gid=1334564098",
                           sheet = " Deployments_IndexOnly",
                           na = c("", "n/a", "#N/A"),
                           col_types = "c")

metadata <- metadata_raw |>
  clean_names() |>
  rename("site" = "x1",
         "logger_id" = "nickname") |>
  separate(relaunch_file_name_recovery_file_name,
           into = c("relaunch_file_name", "recovery_file_name"),
           sep = ",")

metadata <- metadata |>
  mutate(position = tolower(position),
         logger_id = if_else(is.na(logger_id), 
                             str_split(relaunch_file_name, "_", simplify = TRUE)[, 2],
                             logger_id)) |>
  filter(!(str_detect(site, "^20\\d{2}$"))) |>
  mutate(site = tolower(site),
         site = str_remove_all(site, "[^a-zA-Z0-9]")) |>
  # dates
  mutate(launch_date_office = parse_date_time(launch_date_office,
                                              orders = c("ymd", "mdy")),
         initial_deployment_date = parse_date_time(initial_deployment_date,
                                                   orders = c("ymd", "mdy")),
         initial_deployment_time = str_remove(initial_deployment_time, "^~\\s*"),
         initial_deployment_time = parse_date_time(initial_deployment_time,
                                                   orders = c("HM", "I:M p")),
         # Combine deployment date and time
         initial_deployment_datetime = case_when(
           # if no date, datetime = NA
           is.na(initial_deployment_date) ~ as.POSIXct(NA),
           # if no time, use the date and fill 00:00:00 for time
           is.na(initial_deployment_time) ~ ymd_hms(paste(as.Date(initial_deployment_date),
                                                          "00:00:00")),
           # otherwise, combine the two 
           TRUE ~ ymd_hms(paste(as.Date(initial_deployment_date), 
                                format(initial_deployment_time, "%H:%M:%S"))))) |>
  relocate(initial_deployment_datetime, .after = initial_deployment_time)

metadata <- metadata |>
  mutate(relaunch_date = if_else(site == "edmonds" &
                                   logger_id == "DO18" &
                                   relaunch_date == "2025-04-02",
                                 "2025-03-13",
                                 relaunch_date),
         relaunch_date = parse_date_time(relaunch_date,
                                         orders = c("ymd", "mdy")))

metadata <- metadata |>
  mutate(relaunch_recovery_time = if_else(site == "edmonds" &
                                            logger_id == "DO18" &
                                            relaunch_date == "2025-04-02",
                                          "9:30",
                                          relaunch_recovery_time),
         relaunch_recovery_time = parse_date_time(relaunch_recovery_time,
                                                  orders = c("HM", "I:M p")))

metadata <- metadata |>
  mutate( 
    # Combine relauch date and time
    relaunch_recovery_datetime = case_when(
      # if no date, datetime = NA
      is.na(relaunch_date) ~ as.POSIXct(NA),
      # if no time, use the date and fill 00:00:00 for time
      is.na(relaunch_recovery_time) ~ ymd_hms(paste(as.Date(relaunch_date),
                                                    "00:00:00")),
      # otherwise, combine the two 
      TRUE ~ ymd_hms(paste(as.Date(relaunch_date), 
                           format(relaunch_recovery_time, "%H:%M:%S")))), 
    .after = relaunch_recovery_time)

metadata <- metadata |>
  mutate(
    # Relauch Deployment Datetime
    relaunch_deployment_time = str_remove(relaunch_deployment_time, "^~\\s*"),
    relaunch_deployment_time = parse_date_time(relaunch_deployment_time,
                                               orders = c("HM", "I:M p", "I:M:S p")))

metadata <- metadata |>
  mutate(
    relaunch_deployment_datetime = case_when(
      # if no date, datetime = NA
      is.na(relaunch_date) ~ as.POSIXct(NA),
      # if no time, use the date and fill 00:00:00 for time
      is.na(relaunch_deployment_time) ~ ymd_hms(paste(as.Date(relaunch_date),
                                                      "00:00:00")),
      # otherwise, combine the two 
      TRUE ~ ymd_hms(paste(as.Date(relaunch_date), 
                           format(relaunch_deployment_time, "%H:%M:%S")))), 
    .after = relaunch_deployment_time)

metadata <- metadata |>
  mutate(relaunch_data_readout_date = parse_date_time(relaunch_data_readout_date,
                                                      orders = c("ymd", "mdy")))

metadata <- metadata |>
  mutate(recovery_date = parse_date_time(recovery_date,
                                         orders = c("ymd", "mdy")),
         recovery_time = str_remove(recovery_time, "^~\\s*"),
         recovery_time = parse_date_time(recovery_time,
                                         orders = c("HM", "I:M p", "I:M:S p")),
         data_readout_date = parse_date_time(data_readout_date,
                                             orders = c("ymd", "mdy")))

metadata <- metadata |>
  separate(file_upload_date,
           into = c("file_upload_date_1", "file_upload_date_2"),
           sep = ",") |>
  mutate(file_upload_date_1 = parse_date_time(file_upload_date_1,
                                              orders = c("ymd", "mdy")),
         file_upload_date_2 = parse_date_time(file_upload_date_2,
                                              orders = c("ymd", "mdy")))
```

Assumptions:

the relaunch date on this row is incorrect and should actually be 2025-03-13:
Edmonds	BOTTOM	DO18	21556613	12/10/2024	2024-12-11	11:08	2025-04-02	Shuttle	9:30:00 AM @ 3-13	11:45:00 AM	2025-03-14				


Streamline that metadata cleaning into a function:

```{r}
read_and_clean_metadata <- function(metadata_file_url = "https://docs.google.com/spreadsheets/d/1JJ4Vtb_pI9FJRvMYg7pbhQzM6JPcFzGVU3rR9IdYnGQ/edit?gid=1334564098#gid=1334564098",
                                    sheet_name = " Deployments_IndexOnly"){
  
  # Read in metadata sheet from google drive
  metadata_raw <- read_sheet(metadata_file_url,
                             sheet = sheet_name,
                             na = c("", "n/a", "#N/A"),
                             col_types = "c")
  
  # Cleaning
  metadata <- metadata_raw |>
    clean_names() |>
    # Rename nickname to logger_id to match logger file convention
    rename("site" = "x1",
           "logger_id" = "nickname") |>
    separate(relaunch_file_name_recovery_file_name,
             into = c("relaunch_file_name", "recovery_file_name"),
             sep = ",") |>
    # Make position consistently lowercase
    mutate(position = tolower(position),
           # If no logger_id in column, pull from filename
           logger_id = if_else(is.na(logger_id), 
                               str_split(relaunch_file_name, "_", simplify = TRUE)[, 2],
                               logger_id)) |>
    # Remove rows that are year seperators
    filter(!(str_detect(site, "^20\\d{2}$"))) |>
    # Make site name consistently lowercase with no spaces or puncuation
    mutate(site = tolower(site),
           site = str_remove_all(site, "[^a-zA-Z0-9]")) |>
    # Dates
    mutate(launch_date_office = parse_date_time(launch_date_office,
                                                orders = c("ymd", "mdy")),
           initial_deployment_date = parse_date_time(initial_deployment_date,
                                                     orders = c("ymd", "mdy")),
           initial_deployment_time = str_remove(initial_deployment_time, "^~\\s*"),
           initial_deployment_time = parse_date_time(initial_deployment_time,
                                                     orders = c("HM", "I:M p")),
           # Combine deployment date and time
           initial_deployment_datetime = case_when(
             # if no date, datetime = NA
             is.na(initial_deployment_date) ~ as.POSIXct(NA),
             # if no time, use the date and fill 00:00:00 for time
             is.na(initial_deployment_time) ~ ymd_hms(paste(as.Date(initial_deployment_date),
                                                            "00:00:00")),
             # otherwise, combine the two 
             TRUE ~ ymd_hms(paste(as.Date(initial_deployment_date), 
                                  format(initial_deployment_time, "%H:%M:%S"))))) |>
    relocate(initial_deployment_datetime, .after = initial_deployment_time) |>
    mutate(relaunch_date = if_else(site == "edmonds" &
                                     logger_id == "DO18" &
                                     relaunch_date == "2025-04-02",
                                   "2025-03-13",
                                   relaunch_date),
           relaunch_date = parse_date_time(relaunch_date,
                                           orders = c("ymd", "mdy"))) |>
    mutate(relaunch_recovery_time = if_else(site == "edmonds" &
                                              logger_id == "DO18" &
                                              relaunch_date == "2025-04-02",
                                            "9:30",
                                            relaunch_recovery_time),
           relaunch_recovery_time = parse_date_time(relaunch_recovery_time,
                                                    orders = c("HM", "I:M p"))) |>
    mutate( 
      # Combine relauch date and time
      relaunch_recovery_datetime = case_when(
        # if no date, datetime = NA
        is.na(relaunch_date) ~ as.POSIXct(NA),
        # if no time, use the date and fill 00:00:00 for time
        is.na(relaunch_recovery_time) ~ ymd_hms(paste(as.Date(relaunch_date),
                                                      "00:00:00")),
        # otherwise, combine the two 
        TRUE ~ ymd_hms(paste(as.Date(relaunch_date), 
                             format(relaunch_recovery_time, "%H:%M:%S")))), 
      .after = relaunch_recovery_time) |>
    mutate(
      # Relauch Deployment Datetime
      relaunch_deployment_time = str_remove(relaunch_deployment_time, "^~\\s*"),
      relaunch_deployment_time = parse_date_time(relaunch_deployment_time,
                                                 orders = c("HM", "I:M p", "I:M:S p"))) |>
    mutate(
      relaunch_deployment_datetime = case_when(
        # if no date, datetime = NA
        is.na(relaunch_date) ~ as.POSIXct(NA),
        # if no time, use the date and fill 00:00:00 for time
        is.na(relaunch_deployment_time) ~ ymd_hms(paste(as.Date(relaunch_date),
                                                        "00:00:00")),
        # otherwise, combine the two 
        TRUE ~ ymd_hms(paste(as.Date(relaunch_date), 
                             format(relaunch_deployment_time, "%H:%M:%S")))), 
      .after = relaunch_deployment_time) |>
    mutate(relaunch_data_readout_date = parse_date_time(relaunch_data_readout_date,
                                                        orders = c("ymd", "mdy"))) |>
    mutate(recovery_date = parse_date_time(recovery_date,
                                           orders = c("ymd", "mdy")),
           recovery_time = str_remove(recovery_time, "^~\\s*"),
           recovery_time = parse_date_time(recovery_time,
                                           orders = c("HM", "I:M p", "I:M:S p")),
           data_readout_date = parse_date_time(data_readout_date,
                                               orders = c("ymd", "mdy"))) |>
    separate(file_upload_date,
             into = c("file_upload_date_1", "file_upload_date_2"),
             sep = ",") |>
    mutate(file_upload_date_1 = parse_date_time(file_upload_date_1,
                                                orders = c("ymd", "mdy")),
           file_upload_date_2 = parse_date_time(file_upload_date_2,
                                                orders = c("ymd", "mdy")))
  
  return(metadata)
  
}

```


Test out metadata cleaning function
```{r}
metadata <- read_and_clean_metadata()



position <- metadata$position[metadata$site == "jeffersonhead" &
                                metadata$logger_id == "T2" &
                                metadata$initial_deployment_date == as.Date("2023-01-20")]

unique(metadata$site)
unique(all$site)
```


```{r}
# attempt to filter out stuff from metadata... ... ... 
# start with just Jefferson head temp for simplicity
jh <- all |>
  filter(site == "jeffersonhead") |>
  select(c("site", "position", "temp_logger_id", "temp_c", "datetime")) |>
  # add in missing times as NA to complete timeseries
  group_by(site, position) |>
  complete(datetime = seq(min(datetime), max(datetime), by = "15 mins")) |>
  ungroup() |>
  distinct() #|>
#  filter(position == "surface")

# I want to filter out datetime that:
## starts before initial_deployment_datetime in metadata, 
## is between relaunch_recovery_datetime and relaunch_deployment_datetime
## is after recovery_datetime

initial_deployment_date <- metadata$initial_deployment_datetime[
  metadata$site == "edmonds" &
    metadata$logger_id == "T11" &
    metadata$initial_deployment_date == as.Date("2024-06-13")
]
relaunch_recovery_date <- metadata$relaunch_recovery_datetime[
  metadata$site == "edmonds" &
    metadata$logger_id == "T11" &
    metadata$initial_deployment_date == as.Date("2024-06-13")
]
relaunch_deployment_date <- metadata$relaunch_deployment_datetime[
  metadata$site == "edmonds" &
    metadata$logger_id == "T11" &
    metadata$initial_deployment_date == as.Date("2024-06-13")
]
recovery_date <- metadata$recovery_datetime[
  metadata$site == "edmonds" &
    metadata$logger_id == "T11" &
    metadata$initial_deployment_date == as.Date("2024-06-13")
]


test_outofwater_filter <- df_temp |>
  mutate(
    temp_c = case_when(
      datetime <= initial_deployment_date ~ NA_real_,
      datetime >= relaunch_recovery_date & datetime <= relaunch_deployment_date ~ NA_real_,
      datetime >= recovery_date ~ NA_real_,
      TRUE ~ temp_c
    )
  )



ggplot(df_temp) +
  geom_line(aes(x = datetime, y = temp_c, color = position))

ggplot(test_outofwater_filter) +
  geom_line(aes(x = datetime, y = temp_c, color = position))
```

Ok.... let's try the big guy


```{r}
range(data$datetime)
unique(data$site)

# surface temp visual check
logger_data |>
  filter(position == "surface") |>
  ggplot() +
  geom_point(aes(x = datetime, y = tidbit_temp_c, color = temp_logger_id), size = 0.1) +
  facet_wrap(~site)

# surface ph
logger_data |>
  filter(position == "surface") |>
  filter(pH <= 10) |>
  ggplot() +
  geom_point(aes(x = datetime, y = pH, color = ph_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "pH at Surface by Site",
       x = "Date",
       y = "pH") +
  theme_minimal()

# bottom ph
logger_data |>
  filter(position == "bottom") |>
  ggplot() +
  geom_point(aes(x = datetime, y = pH, color = ph_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "pH at Bottom by Site",
       x = "Date",
       y = "pH") +
  theme_minimal()


# surface do
logger_data |>
  filter(position == "surface") |>
  filter(do_conc_mg_per_L >= 0) |>
  ggplot() +
  geom_point(aes(x = datetime, y = do_conc_mg_per_L, color = do_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "Dissolved Oxygen at Surface by Site",
       x = "Date",
       y = "Dissolved Oxygen (mg/L)") +
  theme_minimal()

# bottom do
logger_data |>
  filter(position == "bottom") |>
  filter(do_conc_mg_per_L >= 0) |>
  ggplot() +
  geom_point(aes(x = datetime, y = do_conc_mg_per_L, color = do_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "Dissolved Oxygen at Bottom by Site",
       x = "Date",
       y = "Dissolved Oxygen (mg/L)") +
  theme_minimal()


# bottom wl
logger_data |>
  filter(position == "bottom") |>
  ggplot() +
  geom_point(aes(x = datetime, y = abs_pres_kpa, color = wl_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "Water Level at Bottom by Site",
       x = "Date",
       y = "Absolute Pressure (kpa)") +
  theme_minimal()


# bottom par (raw)
logger_data |>
  filter(position == "bottom") |>
  ggplot() +
  geom_point(aes(x = datetime, y = raw_integrating_light, color = par_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "PAR Raw at Bottom by Site",
       x = "Date",
       y = "Raw Integrating Light") +
  theme_minimal()

# bottom par (calibrated)
logger_data |>
  filter(position == "bottom") |>
  ggplot() +
  geom_point(aes(x = datetime, y = calibrated_integrating_light, color = par_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "PAR Calibrated at Bottom by Site",
       x = "Date",
       y = "Calibrated Integrating Light") +
  theme_minimal()
# urm calibrated is the same as raw?

# surface con
logger_data |>
  filter(position == "surface") |>
  ggplot() +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm, color = con_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "Conductivity at Surface by Site",
       x = "Date",
       y = "Conductivity (µS/cm)") +
  theme_minimal()

# bottom con
logger_data |>
  filter(position == "bottom") |>
  ggplot() +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm, color = con_logger_id), size = 0.1) +
  facet_wrap(~site) +
  labs(title = "Conductivity at Bottom by Site",
       x = "Date",
       y = "Conductivity (µS/cm)") +
  theme_minimal()

# comparing all temp measures
logger_data |>
  select(site, position, datetime, tidbit_temp_c, ph_temp_c, do_temp_c, wl_temp_c, con_temp_c) |>
  pivot_longer(
    cols = c(tidbit_temp_c, ph_temp_c, do_temp_c, wl_temp_c, con_temp_c),
    names_to = "temp_sensor_type",
    values_to = "temperature_c"
  ) |>
  filter(position == "surface",
         temperature_c >= 0,
         temperature_c <= 25) |>
  ggplot(aes(x = datetime, y = temperature_c, color = temp_sensor_type)) +
  geom_line(alpha = 0.7) +
  facet_wrap(~site) +
  labs(
    title = "Temperature Measurements at Surface by Site",
    x = "Date/Time", 
    y = "Temperature (°C)",
    color = "Sensor Type"
  ) +
  theme_minimal()

logger_data |>
  select(site, position, datetime, tidbit_temp_c, ph_temp_c, do_temp_c, wl_temp_c, con_temp_c) |>
  pivot_longer(
    cols = c(tidbit_temp_c, ph_temp_c, do_temp_c, wl_temp_c, con_temp_c),
    names_to = "temp_sensor_type",
    values_to = "temperature_c"
  ) |>
  filter(position == "bottom",
         temperature_c >= 0,
         temperature_c <= 25) |>
  ggplot(aes(x = datetime, y = temperature_c, color = temp_sensor_type)) +
  geom_line(alpha = 0.7) +
  facet_wrap(~site) +
  labs(
    title = "Temperature Measurements at Bottom by Site",
    x = "Date/Time", 
    y = "Temperature (°C)",
    color = "Sensor Type"
  ) +
  theme_minimal()

```


So glad that this is seemingly working so far! Next steps for me:
- Find a way to validate this against some raw files.
- Work on more ways to filter outliers
- Would love to be able to update and grab new files without needing to re-process all of the old ones as well (GOT IT!!)
- Bring in temp from other instruments as well (do we want to include all?)



```{r}
# save what I have for now - may be useful in data meeting tomorrow
# write_rds(please_lord, "all_loggers.rds")
```


```{r}
# Lets try the incremental function
data <- update_logger_data_incremental()
```


---

Manually check a few files that we suspect are duplicates in the drive:
```{r}
ed_ph_1 <- read_csv(here::here("data", "Edmonds_pH5_2023-01-20.csv"))
ed_ph_2 <- read_csv(here::here("data", "Edmonds_pH5_2023-01-20-2.csv"))

library(dataCompareR)

comparison_result <- rCompare(ed_ph_1, ed_ph_2)
summary(comparison_result)

ed_wl_1 <- read_csv(here::here("data", "Edmonds_WL6_2024-09-04.csv"))
ed_wl_2 <- read_csv(here::here("data", "Edmonds_WL6_2024-09-04 copy.csv"))

comparison_result <- rCompare(ed_wl_1, ed_wl_2)
summary(comparison_result)

jh_wl_1 <- read_csv(here::here("data", "JeffersonHead_WL5_2024-09-04.csv"))
jh_wl_2 <- read_csv(here::here("data", "JeffersonHead_WL5_2024-09-04 copy.csv"))

comparison_result <- rCompare(jh_wl_1, jh_wl_2)
summary(comparison_result)

wp_wl_1 <- read_csv(here::here("data", "WingPoint_WL4_2024-09-04.csv"))
wp_wl_2 <- read_csv(here::here("data", "WingPoint_WL4_2024-09-04 copy.csv"))

comparison_result <- rCompare(wp_wl_1, wp_wl_2)
summary(comparison_result)
```


---

```{r}
# Check if you have multiple rows for ANY site/position/datetime combination
duplicates_check <- logger_data |>
  group_by(site, position, datetime) |>
  filter(n() > 1) |>
  ungroup()

nrow(duplicates_check)  # Should tell you how many duplicate rows exist

# If there are duplicates, look at a sample
if(nrow(duplicates_check) > 0) {
  duplicates_check |>
    select(site, position, datetime) |>
    distinct() |>
    head(10)
}
```

```{r}
write_csv(logger_data, here("data", "logger_data.csv"))

```

```{r}
df <- data |>
  filter(position == "other")

unique(df$site)

df <- df |>
  filter(site == "jeffersonhead")


df <- data |>
  filter(position == "foulweatherbluff",
         do_logger_id == "DO16")

"NorthwestNarrows_DO8_2025-02-18.csv" %in% processed_files


```


```{r}
"Edmonds_DNR6428_2023-10-13.CSV" %in% processed_files
"FoulweatherBluff_CON32_2025-02-18.csv" %in% processed_files
"NorthwestNarrows_DO7_2025-05-21.csv" %in% processed_files
```

```{r}
# Load your saved data
data <- readRDS(here::here("data", "logger_data.rds"))

# Check for records from this specific file
data |> 
  filter(site == "edmonds", 
         wl_logger_id == "DNR6428",  # or appropriate logger_id column
         datetime >= as.Date("2023-10-13")) |> 
  nrow()

processed <- readRDS(here::here("data", "processed_files.rds"))
processed <- processed[!processed %in% c("NorthwestNarrows_DO7_2025-05-21.csv")]
saveRDS(processed, here::here("data", "processed_files.rds"))
```

```{r}
# Check total DO7 rows
data |> 
  filter(do_logger_id == "DO7") |> 
  nrow()

# Check date range of DO7
data |> 
  filter(do_logger_id == "DO7") |> 
  summarise(min_date = min(datetime, na.rm = TRUE), 
            max_date = max(datetime, na.rm = TRUE))

# Check if there are NAs in the May-Aug range
data |> 
  filter(do_logger_id == "DO7") |>
  filter(datetime >= as.POSIXct("2025-05-21")) |>
  summarise(
    total_rows = n(),
    na_do_conc = sum(is.na(do_conc_mg_per_L)),
    non_na_do_conc = sum(!is.na(do_conc_mg_per_L))
  )
```


## Jan 2026 Updates Testing

Attempting to update pipeline so end product is separate files for each sensor type

```{r}
# test run!
df <- update_logger_data_incremental(root_folder_id, metadata_file_url, sheet_name, force_reprocess = TRUE)
view(df$temp)

# quick plot to check
ggplot(temp |>
         filter(position == "surface",
                site == "Edmonds")) +
  geom_line(aes(x = datetime, y = tidbit_temp_c, color = issue_flag))

ggplot(con |>
         filter(position == "surface",
                site == "Edmonds",
                issue_flag == "Fouling")) +
  geom_line(aes(x = datetime, y = high_range_microsiemens_per_cm, color = issue_flag))
```

cool! now ... 

time to work through flagging issues. I want to

- filter out days where loggers are being messed with (deployment, relaunch, and recovery days) - done
- remove anything with the following flags from the metadata:
  - "Data- Invalid", "Instrument- Recovered from bottom"
- Add a column with the issue flag - done
- Add a column with any notes - done
- Add flags for points that are in the top and bottom 1% of data (look for outliers) - did this, do not think it is helpful
- Add flags for points where the absolute difference from the previous observation is in the top 1% of all absolute differences - also did this... still wondering about when this might be helpful, not ready to toss out yet

sensor specific:
- DO cannot be < 0

I think then I will write a separate script that will walk through manually checking fouling flags.



```{r}
# Test 1% flags
flagged_do <- do |>
  arrange(site, position, datetime) |>
  group_by(site, position) |>
  mutate(
    # Flag outliers
    outlier_flag = !is.na(do_conc_mg_per_L) &
      (do_conc_mg_per_L < quantile(do_conc_mg_per_L, 0.01, na.rm = TRUE) |
         do_conc_mg_per_L > quantile(do_conc_mg_per_L, 0.99, na.rm = TRUE)),
    
    # Flag big jumps
    abs_diff = abs(do_conc_mg_per_L - lag(do_conc_mg_per_L)),
    spike_flag = !is.na(abs_diff) & 
      abs_diff > quantile(abs_diff, 0.99, na.rm = TRUE)
  )


# Create a separate dataframe of flagged periods
issue_periods <- con |>
  filter(site == "Jefferson Head",
         position == "surface",
         !is.na(issue_flag)) |>
  arrange(datetime) |>
  mutate(
    # Calculate time gap from previous row
    time_gap  = as.numeric(difftime(datetime, lag(datetime), units = "hours")),
    # Start a new group if the flag changes OR there is a gap larger than expected
    # (e.g. > 1 hour for 15-min data, adjust threshold if needed)
    new_group = is.na(time_gap) | issue_flag != lag(issue_flag, default = "") | time_gap > 1,
    group_id  = cumsum(new_group)
  ) |>
  group_by(site, position, issue_flag, group_id) |>
  summarise(start = min(datetime),
            end   = max(datetime),
            .groups = "drop")

issue_periods <- issue_periods |>
  bind_rows(
    tibble(
      site           = "Jefferson Head",
      position       = "surface",
      issue_flag     = "Data- Incomplete file",
      group_id       = NA_real_,
      start          = as.POSIXct("2025-06-05"),
      end            = as.POSIXct("2025-08-26")
    )
  )

# plot
jh_surface_con_issues <- ggplot(con |>
         filter(site == "Jefferson Head",
                position == "surface") |>
         mutate(year = year(datetime)),
       aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  geom_rect(data = issue_periods |> mutate(year = year(start)),
            aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf, fill = issue_flag),
            inherit.aes = FALSE, alpha = 0.2) +
  geom_point(alpha = 0.3, size = 0.8) +
  labs(title = "Jefferson Head, Surface, Conductivity (Raw)",
       subtitle = "Data issues for deployments highlighted behind points",
       fill = "Issue Flag") +
  facet_wrap(~ year, scales = "free_x", ncol = 1) +
  theme_minimal(base_size = 12) +
  theme(plot.title.position = "plot")

ggsave(here::here("figures", "jh_surface_con_issues.png"), jh_surface_con_issues,
       width = 12, height = 7)

```

## Issue plots for each site / sensor type / position

```{r}
# look at JH surface CON for flag plot troubleshooting
jh_surf_con <- logger_data_con |>
  filter(site == "Jefferson Head",
         position == "surface")

# something werid with joining in flags ): some troubleshooting:
test_meta <- read_and_clean_metadata(metadata_file_url, sheet_name) |>
  filter(site == "Jefferson Head", position == "surface", logger_type == "conductivity") |>
  select(site, position, logger_type, in_water_date, out_of_water_date, issue_flag, comments) |>
  mutate(in_water_date = as.POSIXct(in_water_date),
         out_of_water_date = as.POSIXct(out_of_water_date))
# test the join
jh_surf_con |>
  left_join(test_meta |> rename(flag_fill = issue_flag, comments_fill = comments),
            join_by(site, position, logger_type,
                    datetime > in_water_date,
                    datetime < out_of_water_date)) |>
  select(datetime, issue_flag, flag_fill) |>
  filter(datetime >= "2025-06-03", datetime <= "2025-06-06") |>
  print(n = 100)

# hmm. going to try flipping the order of flag grabs in coalese()
# i could grab all the flags at the end, but i still kind of want to make this more efficient later, which would mean only going through some of the data and filling / grabbing flags at the end. so i will leave for now

# Get unique site/position combos in con
site_pos_combos <- temp |> distinct(site, position)

plot_sensor_issues <- function(data, site_name, pos, sensor_col, y_label, title_sensor) {
  
  # Filter to this site/position
  plot_data <- data |>
    filter(site == site_name,
           position == pos)
  
  # Skip if no data for this combo
  if (nrow(plot_data) == 0) {
    message(paste("No data found for:", site_name, pos, "- skipping"))
    return(NULL)
  }
  
  # Build flagged periods
  issue_periods <- plot_data |>
    filter(!is.na(issue_flag)) |>
    arrange(datetime) |>
    mutate(
      time_gap  = as.numeric(difftime(datetime, lag(datetime), units = "hours")),
      new_group = is.na(time_gap) | issue_flag != lag(issue_flag, default = "") | time_gap > 1,
      group_id  = cumsum(new_group)
    ) |>
    group_by(site, position, issue_flag, group_id) |>
    summarise(start = min(datetime),
              end   = max(datetime),
              .groups = "drop")
  
  # Plot
  ggplot(plot_data |> mutate(year = year(datetime)),
         aes(x = datetime, y = .data[[sensor_col]])) +
    geom_rect(data = issue_periods |> mutate(year = year(start)),
              aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf, fill = issue_flag),
              inherit.aes = FALSE, alpha = 0.2) +
    geom_point(alpha = 0.3, size = 0.8) +
    labs(title    = paste0(site_name, ", ", str_to_title(pos), ", ", title_sensor, " (Raw)"),
         subtitle = "Data issues for deployments highlighted behind points",
         y        = y_label,
         fill     = "Issue Flag") +
    facet_wrap(~ year, 
               scales = "free_x", 
               ncol = 1) +
    theme_minimal(base_size = 12) +
    theme(plot.title.position = "plot")
}

# Generate a plot for each site/position combo in con
temp_plots <- pmap(site_pos_combos, function(site, position) {
  plot_sensor_issues(temp, site, position,
                     sensor_col   = "tidbit_temp_c",
                     y_label      = "Temperature (°C)",
                     title_sensor = "Temperature")
})

# Name the list for easy reference
names(temp_plots) <- paste(site_pos_combos$site, site_pos_combos$position, sep = " - ")

# View them one at a time by index or name
con_plots[[1]]
con_plots[["Jefferson Head - surface"]]
con_plots[["Squaxin Island - bottom"]]

# Or scroll through all at once
walk(temp_plots[!sapply(temp_plots, is.null)], print)


#hmm... why no 2023 data showing for wing point surface con?
wp_con <- logger_data_con |>
  filter(site == "Wing Point",
         position == "surface")

# Squaxin island surface CON fouling note:
# The deployment that is 

# Con check
con |>
  filter(site == "Squaxin Island",
         position == "bottom",
         con_logger_id == "CON17") |>
  distinct(issue_flag)

metadata |>
  filter(site == "Squaxin Island",
         position == "bottom",
         logger_id == "CON17")

metadata |>
  filter(site == "Squaxin Island",
         position == "bottom") |>
  select(site, position, logger_id, deployment_type, in_water_date, out_of_water_date, issue_flag)
```

3/3/26 - leaving off here. things are wonky bringing in issue flags. need an indication in the metadata of sensor type to match with each csv. otherwise it will pull flags from all site/position/in water date combos... aka the entire sensor package

going to add a column in when I am cleaning data in pipeline, using the nickname code. will require whoever names these to stay consistent with the naming scheme (e.g., conductivity loggers need to stay CON##)

## Reworking metadata

Code testing converting the metadata to tidy format before ingesting as a function into the pipeline.

```{r}
# Read in metadata 
metadata_raw <- read_sheet(metadata_file_url,
                             sheet = sheet_name,
                             na = c("", "n/a", "#N/A"),
                             col_types = "c")
```


```{r}
# Some general cleaning pulled from existing function
metadata <- metadata_raw |>
  clean_names() |>
  # Rename nickname to logger_id to match logger file convention
  rename("logger_id" = "nickname") |>
  # Make position consistently lowercase
  mutate(position = tolower(position)) |>
  # Remove rows that are year separators
  filter(!(str_detect(site, "^20\\d{2}$"))) |>
  # Make site name capital with space. e.g., North Beach
  mutate(site = str_replace_all(site, "(?<=[a-z])(?=[A-Z])", " ")) |>
  # Parse dates from varying formats
  mutate(launch_date_office = parse_date_time(launch_date_office,
                                              orders = c("ymd", "mdy")),
         initial_deployment_date = parse_date_time(initial_deployment_date,
                                                   orders = c("ymd", "mdy")))

# Select columns to keep
metadata <- metadata |>
  select(c(site, position, logger_id, sn, initial_deployment_date, relaunch_date,
           recovery_date, issue_flag_deployment, issue_flag_relaunch,
           comments_for_initial_deployment, comments_for_relaunch_deployment)) |>
  rename("serial_number" = "sn")
```

To make deployment and relaunch have their own rows, I am going to first split the metadata into two dataframes, one for inital and one for relaunch. then i will stack the rows

```{r}
# Make initial file
initial <- metadata |>
  mutate(deployment_type = "initial",
         in_water_date = initial_deployment_date,
         # out of water date is either relaunch date, 
         # or if there was no relaunch, it is recovery date.
         # coalesce() finds the first non-missing value at each position
         out_of_water_date = coalesce(relaunch_date, recovery_date),
         issue_flag = issue_flag_deployment,
         comments = comments_for_initial_deployment) |>
  select(site, position, logger_id, serial_number,
         deployment_type, in_water_date, out_of_water_date,
         issue_flag, comments) |>
  # make sure dates are dates
  mutate(out_of_water_date = as.Date(out_of_water_date),
         in_water_date = as.Date(in_water_date))

# Make relaunch file
relaunch <- metadata |>
  # Remove rows when sensor was not relaunched
  filter(!is.na(relaunch_date)) |>
  mutate(deployment_type = "relaunch",
         in_water_date = relaunch_date,
         out_of_water_date = recovery_date,
         issue_flag = issue_flag_relaunch,
         comments = comments_for_relaunch_deployment) |>
  select(site, position, logger_id, serial_number,
         deployment_type, in_water_date, out_of_water_date,
         issue_flag, comments) |>
  # make sure dates are dates
  mutate(out_of_water_date = as.Date(out_of_water_date),
         in_water_date = as.Date(in_water_date))

# Combine initial and relaunch files
metadata_long <- bind_rows(initial, relaunch) |>
  arrange(site, position, logger_id, in_water_date)
```

Test from updated function:

```{r}
metadata <- read_and_clean_metadata(metadata_file_url, sheet_name)
```

I think this is working as expected! Now I need to change the logic in the logger csv cleaning to match new metadata style



---

```{r}
ph |>
 filter(site %in% c("Edmonds", "Centennial Park", "Wing Point"),
        position == "bottom") |>
  ggplot(aes(x = datetime, y = ph_temp_c)) +
  geom_line() +
  facet_wrap(~site)

cp <- ph |>
  filter(site == "Centennial Park",
         position == "bottom")

unique(cp$issue_flag)

ed <- ph |>
  filter(site == "Edmonds",
         position == "bottom")

unique(ed$issue_flag)

wp <- ph |>
  filter(site == "Wing Point",
         position == "bottom")


plot_issue_flags(wp, "ph_temp_c", "sst", "temp")

ed <- ed |>
  mutate(tidbit_temp_c = case_when(issue_flag == "Instrument- Recovered from bottom" ~ NA_real_,
                                   .default = tidbit_temp_c))

wp %>%
  arrange(datetime) %>%
  filter(!is.na(ph_temp_c)) %>%
  mutate(
    gap_days = as.numeric(datetime - lag(datetime), units = "days"),
    grp = cumsum(coalesce(gap_days > 2, FALSE))
  ) %>%
  summarise(
    start = min(datetime),
    end = max(datetime),
    .by = grp
  )
```

# Test new metadata function for reformatted tidy metadata sheet

9/4/2026

```{r}
read_and_clean_metadata(metadata_file_url = metadata_file_url,
                        sheet_name = sheet_name)
```


