---
title: "prep_for_dnr"
format: html
---

Script to prepare data for sharing with DNR for sensor comparisons.

**Think of including:**

-   temp
-   salinity
-   light
-   pressure

all from the surface and benthos when available.

**Share data for:**

-   Wing Pt, 6-14-24 to 2-26-25

    -   Temp: surface and bottom ready to go!

-   Edmonds, 6-18-2024 to 2-18-25

     -   Temp: surface and bottom ready to go!

-   Squaxin, 9-25-24 to 8-21-25

-   Squaxin, 11-15-25 to 3-9-26+

*BUT* There is likely more overlap for metrics other than SST. First let's see what we can offer for their deployment periods

**Prep work:**

-   Confirm that issue flags are matching correctly to time frames
    -   Most recent full data update (4/1/2026) issue flag matching **not** working.
    -   Need to:
        1.  update pipeline to accommodate new (improved) metadata format and
        2.  run pipeline (passive, but time consuming)
    -   Note: sites managed by partners still using old (wide) metadata format
    -   **Decide:** Manually check issues for requested data and update pipeline later? Or use as excuse to work on pipeline now, and further delay data sharing? --> MANUALLY CHECKING ISSUES
-   Remove "bad" data flags
-   Have all PAR been calibrated for these deployments?
-   Do we share conductivity, despite knowing that values are off?
-   What associated metadata do I need to write?

## Setup

```{r}
# load libraries ----
library(tidyverse)
library(here)

# load data ----
# note: using data updated on 4/1/2026
temp <- readRDS(here("data", "logger_data_temp.rds"))
salinity <- readRDS(here("data", "logger_data_con.rds"))
light <- readRDS(here("data", "logger_data_par.rds"))
pressure <- readRDS(here("data", "logger_data_wl.rds"))
ph <- readRDS(here("data", "logger_data_ph.rds")) # best bottom temp data comes from pH sensor
metadata <- read_csv(here("data", "metadata.csv")) # metadata from 7/27/2026
```

## Temp

#### Wing Point

6-14-24 to 2-26-25

**Surface**

```{r}
# Filter to site & date range ----
wing_pt_temp_surface <- temp |>
  filter(site == "Wing Point",
         between(datetime, ymd_hms("2024-06-14 00:00:00"), ymd_hms("2025-02-26 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(wing_pt_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```


**Bottom**

```{r}
# Check overlap with DNR range ---- 
# DNR range: 3-19-24 to 2-26-25
bott_temp_wp <- ph |>
  filter(site == "Wing Point",
         datetime >= ymd_hms("2024-03-19 00:00:00") &
           datetime <= ymd_hms("2025-02-26 00:00:00"),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# visual check
ggplot(bott_temp_wp) +
  geom_point(aes(x = datetime, y = temp_c))
```


```{r}
# combine surface and bottom at wing pt
wing_pt_temp <- bind_rows(wing_pt_temp_surface, bott_temp_wp)

# check combine
ggplot(wing_pt_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Check issue flags

```{r}
# function to create issue flag plots ----
issue_plot_builder <- function(data, site_name, pos, sensor_col, y_label, title_sensor) {
  
  # Filter to this site/position
  plot_data <- data |>
    filter(site == site_name,
           position == pos)

  
  # Build flagged periods
  issue_periods <- plot_data |>
    filter(!is.na(issue_flag)) |>
    arrange(datetime) |>
    mutate(
      time_gap = as.numeric(difftime(datetime, lag(datetime), units = "hours")),
      new_group = is.na(time_gap) | issue_flag != lag(issue_flag, default = "") | time_gap > 1,
      group_id = cumsum(new_group)
    ) |>
    group_by(site, position, issue_flag, group_id) |>
    summarise(start = min(datetime),
              end = max(datetime),
              .groups = "drop")
  
  # Plot
  ggplot(plot_data |> 
           mutate(year = year(datetime)),
         aes(x = datetime, y = .data[[sensor_col]])) +
    geom_rect(data = issue_periods |> 
                mutate(year = year(start)),
              aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf, fill = issue_flag),
              inherit.aes = FALSE, alpha = 0.2) +
    geom_point(alpha = 0.3, size = 0.8) +
    labs(title = paste0(site_name, ", ", str_to_title(pos), ", ", title_sensor, " (Raw)"),
         subtitle = "Data issues for deployments highlighted behind points",
         y = y_label,
         fill = "Issue Flag") +
    facet_wrap(~ year, 
               scales = "free_x", 
               ncol = 1) +
    theme_minimal(base_size = 12) +
    theme(plot.title.position = "plot")
}
```

```{r}
# check for issues
issue_plot_builder(wing_pt_temp, "Wing Point", "surface", "temp_c", "C", "temp")
```

```{r}
# check for issues
issue_plot_builder(wing_pt_temp, "Wing Point", "bottom", "temp_c", "C", "temp")
```

**Wing Point temp data good to go**

Manually check issues against metadata

```{r}
wp_meta_temp_surface <- metadata |>
  filter(site == "Wing Point",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-06-13"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags for surface
```
```{r}
wp_meta_temp_bottom <- metadata |>
  filter(site == "Wing Point",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2024-06-13"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags for bottom
```


#### Edmonds

6-18-2024 to 2-18-25

**Surface**

```{r}
# Check overlap with DNR range ---- 
# DNR range: 2-6-24 to 2-18-25
surf_temp_ed <- temp |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00")) |>
  rename("temp_c" = "tidbit_temp_c")

# visual check
ggplot(surf_temp_ed) +
  geom_point(aes(x = datetime, y = temp_c))
```

```{r}
# Filter to site & date range ----
edmonds_temp_surface <- temp |>
  filter(site == "Edmonds",
         between(datetime, ymd_hms("2024-06-18 00:00:00"), ymd_hms("2025-02-18 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(edmonds_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```

**Bottom**

```{r}
# Check overlap with DNR range ---- 
# DNR range: 2-6-24 to 2-18-25
bott_temp_ed <- ph |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# visual check
ggplot(bott_temp_ed) +
  geom_point(aes(x = datetime, y = temp_c))
```


```{r}
# combine surface and bottom
edmonds_temp <- bind_rows(edmonds_temp_surface, bott_temp_ed)

# check combine
ggplot(edmonds_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Manually check issues against metadata

```{r}
ed_meta_temp_surface <- metadata |>
  filter(site == "Edmonds",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-06-10"),
         in_water_date <= as.Date("2025-02-19"))

# 1 issue flag: failure to offload. was later offloaded at office, so no action needed.
```

```{r}
ed_meta_temp_bottom <- metadata |>
  filter(site == "Edmonds",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2023-12-06"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags
```

**Edmonds temp data good to go for surface and bottom**

#### Squaxin

9-25-24 to 8-21-25;

11-15-25 to 3-9-26+

**Surface**

Range 1:
```{r}
# Filter to site & date range ----
squaxin_temp_surface <- temp |>
  filter(site == "Squaxin Island",
         between(datetime, ymd_hms("2024-09-25 00:00:00"), ymd_hms("2025-08-21 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(squaxin_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```

Range 2:
```{r}
# Filter to site & date range ----
squaxin_temp_surface2 <- temp |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2025-11-15 00:00:00")) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(squaxin_temp_surface2) +
  geom_point(aes(x = datetime, y = temp_c))
```


**Bottom**

```{r}
# Check overlap with DNR range ---- 
# DNR range: 7-7-21 to 5-27-26
bott_temp_sqx <- ph |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2021-07-21 00:00:00") &
           datetime <= ymd_hms("2026-05-27 00:00:00"),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# visual check
ggplot(bott_temp_sqx) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position)
```

```{r}
# Filter to site & date range ----
squaxin_temp_bottom2 <- ph |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2025-11-15 00:00:00"),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# check filter
ggplot(squaxin_temp_bottom2) +
  geom_point(aes(x = datetime, y = temp_c))
```

```{r}
# combine surface and bottom
squaxin_temp <- bind_rows(squaxin_temp_surface, squaxin_temp_surface2,
                          bott_temp_sqx)

# check combine
ggplot(squaxin_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Manually check issues against metadata

```{r}
sqx_meta_temp_surface <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-09-20"),
         in_water_date <= as.Date("2025-08-22"))

# No issue flags

sqx_meta_temp_surface2 <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "temperature",
         in_water_date >= as.Date("2025-11-10"))

# No issue flags
```

```{r}
sqx_meta_temp_bottom <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2024-09-20"),
         in_water_date <= as.Date("2025-08-22"))

# No issue flags

sqx_meta_temp_bottom2 <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2025-11-10"))

# No issue flags
```

Squaxin temp data good to go. 

### Combine all temp data

```{r}
# bind temp data ----
temperature <- bind_rows(wing_pt_temp, edmonds_temp, squaxin_temp) |>
  select(site, position, datetime, temp_c, comments)

# check combine
ggplot(temperature) +
  geom_point(aes(x = datetime, y = temp_c, color = site),
             alpha = 0.5, size = 0.2) +
  facet_wrap(~position)

# check ranges
temp_check <- temperature |>
  group_by(site) |>
  reframe(range = range(datetime))
```

```{r}
# export temp data
# write_csv(temperature, here("data", "processed", "temperature.csv"))
```

```{r}
# clean environment
rm(list = setdiff(ls(), c("salinity", "light", "pressure", "metadata")))
```

------------------------------------------------------------------------

## Salinity

#### Wing Point

```{r}
# Check overlap with DNR range ---- 
# DNR range: 3-19-24 to 2-26-25
salinity_wp <- salinity |>
  filter(site == "Wing Point",
         datetime >= ymd_hms("2024-03-19 00:00:00") &
           datetime <= ymd_hms("2025-02-26 00:00:00"))

# visual check
ggplot(salinity_wp) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  facet_wrap(~position)
```

Manually check issues against metadata

```{r}
# surface
wp_meta_con_surface <- metadata |>
  filter(site == "Wing Point",
         logger_type == "conductivity",
         position == "surface",
         in_water_date >= as.Date("2024-03-10"),
         in_water_date <= as.Date("2025-02-20"))

# Fouling flag for 2024-09-04 to 2024-12-11




# bottom
wp_meta_con_bottom <- metadata |>
  filter(site == "Wing Point",
         logger_type == "conductivity",
         position == "bottom",
         in_water_date >= as.Date("2024-03-10"),
         in_water_date <= as.Date("2025-02-20"))

# No issues at benthos
```

We can offer conductivity data for:
- Surface: 6-14-2024 to 2-26-2025
- Bottom: 3-19-2024 to 2-26-2025

Original requested range:
- 6-14-24 to 2-26-25

So, same for surface, slightly extended for bottom.

#### Edmonds

```{r}
# Check overlap with DNR range ---- 
# DNR range: 2-6-24 to 2-18-25
salinity_ed <- salinity |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"))

# visual check
ggplot(salinity_ed) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  facet_wrap(~position)
```

Manually check issues against metadata

```{r}
# surface
ed_meta_con_surface <- metadata |>
  filter(site == "Edmonds",
         logger_type == "conductivity",
         position == "surface",
         in_water_date >= as.Date("2023-12-01"),
         in_water_date <= as.Date("2025-02-10"))

# Issue flag: 2024-04-03 to 2024-06-17 recovered from bottom
# All other surface housings at Edmonds were recovered from bottom 2023-12-14 to 2024-04-03. Also likely here. 
# Fouling flag: 2024-09-04 to 2024-12-11


# bottom
ed_meta_con_bottom <- metadata |>
  filter(site == "Edmonds",
         logger_type == "conductivity",
         position == "bottom",
         in_water_date >= as.Date("2023-12-01"),
         in_water_date <= as.Date("2025-02-10"))

# No issues at benthos
```

We can offer conductivity data for:
- Surface: 2024-06-18 to 2025-02-18
- Bottom: 2024-02-06 to 2025-02-18

Original requested range:
- 6-18-2024 to 2-18-25

```{r}
# Filter to "good" data
salinity_ed_surf <- salinity |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-06-18 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"),
         position == "surface")

salinity_ed_bottom <- salinity |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"),
         position == "bottom")

# combine surface and bottom at wing pt
salinity_ed <- bind_rows(salinity_ed_surf, salinity_ed_bottom)

# check combine
ggplot(salinity_ed) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  facet_wrap(~position, ncol = 1)
```



#### Squaxin

```{r}
# Check overlap with DNR range ---- 
# DNR range: 7-7-21 to 5-27-26
salinity_sqx <- salinity |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2021-07-21 00:00:00") &
           datetime <= ymd_hms("2026-05-27 00:00:00"))

# visual check
ggplot(salinity_sqx) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  facet_wrap(~position)
```

Manually check issues against metadata

```{r}
# surface
sqx_meta_con_surface <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "conductivity",
         position == "surface"#,
         # in_water_date >= as.Date("2023-12-01"),
         # in_water_date <= as.Date("2025-02-10")
         )

# Only 1 fouling flag 2025-03-07 to 2025-05-15


# bottom
sqx_meta_con_bottom <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "conductivity",
         position == "bottom"#,
         # in_water_date >= as.Date("2023-12-01"),
         # in_water_date <= as.Date("2025-02-10")
         )

# Bad data from 2025-08-22 to 2026-03-10
```

We can offer conductivity data for:
- Surface: 2024-09-25 to 2026-03-09
- Bottom: 2024-09-25 to 2025-08-22

Original requested range:
- 11-15-25 to 3-9-26+

```{r}
# Filter to final ranges
sal_sqx_surf <- salinity_sqx |>
  filter(datetime >= ymd_hms("2024-09-25 00:00:00") &
           datetime <= ymd_hms("2026-03-09 00:00:00"),
         position == "surface")

ggplot(sal_sqx_surf) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm))

sal_sqx_bot <- salinity_sqx |>
  filter(datetime >= ymd_hms("2024-09-25 00:00:00") &
           datetime <= ymd_hms("2025-08-22 00:00:00"),
         position == "bottom")

ggplot(sal_sqx_bot) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm))

salinity_sqx <- bind_rows(sal_sqx_surf, sal_sqx_bot)

# visual check
ggplot(salinity_sqx) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm)) +
  facet_wrap(~position)
```
### Combine all con data

```{r}
# bind con data ----
conductivity <- bind_rows(salinity_wp, salinity_ed, salinity_sqx) |>
  rename("temp_c" = "con_temp_c") |>
  select(site, position, datetime, high_range_microsiemens_per_cm,
         temp_c,comments)

# check combine
ggplot(conductivity) +
  geom_point(aes(x = datetime, y = high_range_microsiemens_per_cm, color = site),
             alpha = 0.5, size = 0.2) +
  facet_wrap(~position)

# check ranges
con_check <- conductivity |>
  group_by(site) |>
  reframe(range = range(datetime))
```

```{r}
# save file
# write_csv(conductivity,
#           here("data", "processed", "conductivity.csv"))
```

```{r}
# clean environment
rm(list = setdiff(ls(), c("light", "pressure", "metadata")))
```

## Light

Light is only collected at the benthos.

#### Wing Point

6-14-24 to 2-26-25

```{r}
# Check overlap with DNR range ---- 
# DNR range: 3-19-24 to 2-26-25
light_wp <- light |>
  filter(site == "Wing Point",
         datetime >= ymd_hms("2024-03-19 00:00:00") &
           datetime <= ymd_hms("2025-02-26 00:00:00"))

# visual check
ggplot(light_wp) +
  geom_point(aes(x = datetime, y = raw_integrating_light))
```
Data starts 2024-09-05

Manually check issues against metadata

```{r}
# surface
wp_meta_light <- metadata |>
  filter(site == "Wing Point",
         logger_type == "par",
         in_water_date >= as.Date("2024-09-01"),
         in_water_date <= as.Date("2025-02-20"))
```

Only 1 flag for fouling. 

Checking serial number against calibration estimated values:
- sensor 13063 (nickname = PSRF03) = 0.04648728467
- sensor 15604 (nickname = PAR2) = 0.07560545193

```{r}
# calibrate par values ----
light_wp <- light_wp |>
  filter(datetime >= ymd_hms("2024-09-05 00:00:00") &
           datetime <= ymd_hms("2025-02-26 00:00:00")) |>
  mutate(calibrated_integrating_light = case_when(
    logger_id == "PSRF03" ~ raw_integrating_light * 0.04648728467,
    logger_id == "PAR2" ~ raw_integrating_light * 0.07560545193,
    .default = calibrated_integrating_light
  ))

# visual check
ggplot(light_wp) +
  geom_point(aes(x = datetime, y = calibrated_integrating_light))
```

Good

#### Edmonds

```{r}
# Check overlap with DNR range ---- 
# DNR range: 2-6-24 to 2-18-25
light_ed <- light |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"))

# visual check
ggplot(light_ed) +
  geom_point(aes(x = datetime, y = raw_integrating_light))
```

```{r}
ed_meta_light <- metadata |>
  filter(site == "Edmonds",
         logger_type == "par",
         in_water_date >= as.Date("2023-12-01"),
         in_water_date <= as.Date("2025-02-10"))
```

2024-06-17 to 2024-09-04 instrument offload fail
next deployment not until 2025-01-14

No other issue flags

Checking calibration

15605 (nickname = PAR3) 0.08377513014
6428 (nickname = DNR6428) 0.0586289299
13063 (nickname = PSRF03) 0.04648728467

2025-01-15 2025-02-18

```{r}
# Filter dates and calibrate
light_ed <- light_ed |>
  # filter(datetime >= ymd_hms("2024-02-06 00:00:00") &
  #          datetime <= ymd_hms("2024-06-12 00:00:00"),
  #        datetime >= ymd_hms("2025-01-15 00:00:00") &
  #          datetime <= ymd_hms("2025-02-18 00:00:00")) |>
  filter(!between(datetime, ymd_hms("2024-06-12 00:00:00"), ymd_hms("2025-01-15 00:00:00"))) |>
  mutate(calibrated_integrating_light = case_when(
    logger_id == "PAR3" ~ raw_integrating_light * 0.08377513014,
    logger_id == "DNR6428" ~ raw_integrating_light * 0.0586289299,
    logger_id == "PSRF03" ~ raw_integrating_light * 0.04648728467,
    .default = calibrated_integrating_light
  ))

# visual check
ggplot(light_ed) +
  geom_point(aes(x = datetime, y = calibrated_integrating_light))
```


#### Squaxin

```{r}
# Check overlap with DNR range ---- 
# DNR range: 7-7-21 to 5-27-26
light_sqx <- light |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2021-07-21 00:00:00") &
           datetime <= ymd_hms("2026-05-27 00:00:00"))

# visual check
ggplot(light_sqx) +
  geom_point(aes(x = datetime, y = raw_integrating_light))
```

```{r}
sqx_meta_light <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "par",
         in_water_date >= as.Date("2021-07-01"),
         in_water_date <= as.Date("2026-05-20"))
```

Some no data issue flags, but all data present

Check calibrations:
15603 (PAR1) NOT CALIBRATED
13065 (PSRF5) 0.0598230157
13061 (PSRF1) 0.1328461756
16979 (PAR8) NOT CALIBRATED
15606 (PAR4) NOT CALIBRATED

```{r}
light_sqx <- light_sqx |>
  filter(datetime >= ymd_hms("2024-12-07 00:00:00") &
           datetime <= ymd_hms("2025-05-14 00:00:00")) |>
  mutate(calibrated_integrating_light = case_when(
    logger_id == "PSRF5" ~ raw_integrating_light * 0.0598230157,
    logger_id == "PSRF1" ~ raw_integrating_light * 0.1328461756,
    .default = calibrated_integrating_light
  ))

# visual check
ggplot(light_sqx) +
  geom_point(aes(x = datetime, y = calibrated_integrating_light))
```

### Combine all light data

```{r}
# bind light data ----
light <- bind_rows(light_wp, light_ed, light_sqx) |>
  select(site, position, datetime, logger_id,
         raw_integrating_light, calibrated_integrating_light,
         comments)

# check combine
ggplot(light) +
  geom_point(aes(x = datetime, y = calibrated_integrating_light, color = site),
             alpha = 0.5, size = 0.2) # hmm

# check ranges
light_check <- light |>
  group_by(site) |>
  reframe(range = range(datetime))
```

```{r}
# save file
# write_csv(light,
#           here("data", "processed", "light.csv"))
```

```{r}
# clean environment
rm(list = setdiff(ls(), c("pressure", "metadata")))
```

## Pressure

#### Wing Point

```{r}
# Check overlap with DNR range ---- 
# DNR range: 3-19-24 to 2-26-25
pressure_wp <- pressure |>
  filter(site == "Wing Point",
         datetime >= ymd_hms("2024-03-19 00:00:00") &
           datetime <= ymd_hms("2025-02-26 00:00:00"))

# visual check
ggplot(pressure_wp) +
  geom_point(aes(x = datetime, y = abs_pres_kpa))
```

```{r}
# check metadata issue flags
wp_meta_pres <- metadata |>
  filter(site == "Wing Point",
         logger_type == "water level",
         in_water_date >= as.Date("2023-12-01"),
         in_water_date <= as.Date("2025-02-20"))
```

No issue flags

range available: 2024-03-19 to 2025-02-26

#### Edmonds

```{r}
# Check overlap with DNR range ---- 
# DNR range: 2-6-24 to 2-18-25
pres_ed <- pressure |>
  filter(site == "Edmonds",
         datetime >= ymd_hms("2024-02-06 00:00:00") &
           datetime <= ymd_hms("2025-02-18 00:00:00"))

# visual check
ggplot(pres_ed) +
  geom_point(aes(x = datetime, y = abs_pres_kpa))
```

```{r}
# check metadata issue flags
ed_meta_pres <- metadata |>
  filter(site == "Edmonds",
         logger_type == "water level",
         in_water_date >= as.Date("2023-12-01"),
         in_water_date <= as.Date("2025-02-20"))
```

No issue flags

date range: 2024-02-06 to 2025-02-18

#### Squaxin

```{r}
# Check overlap with DNR range ---- 
# DNR range: 7-7-21 to 5-27-26
pres_sqx <- pressure |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2021-07-21 00:00:00") &
           datetime <= ymd_hms("2026-05-27 00:00:00"))

# visual check
ggplot(pres_sqx) +
  geom_point(aes(x = datetime, y = abs_pres_kpa))
```
```{r}
# check metadata issue flags
sqx_meta_pres <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "water level",
         in_water_date >= as.Date("2021-07-21"),
         in_water_date <= as.Date("2026-05-27"))
```

ranges: 2024-09-25 to 2025-08-21, 2025-11-15 to 2026-03-09
Missing file because named wrong in drive - fixing now !! 

```{r}
# fill hole in data ----

# read in missing file
sqx_fix <- read_csv(here("data", "SquaxinIsland_WLBT1_2025-08-22.csv")) |>
  janitor::clean_names()

# cleaning steps
# parse date time
sqx_fix <- sqx_fix |>
      mutate(datetime = parse_date_time(date_time_pdt, 
                                        orders = c("m/d/y I:M:S p", 
                                                   "m/d/y HMS", 
                                                   "m/d/y HM")))
# filter to missing dates when logger is in water
sqx_fix <- sqx_fix |>
  filter(datetime >= ymd_hms("2025-08-23 00:00:00") &
           datetime < ymd_hms("2025-11-14 00:00:00"))

# rename cols and add missing
sqx_fix <- sqx_fix |>
  mutate(wl_temp_c = temperature_c,
         abs_pres_kpa = absolute_pressure_k_pa,
         site = "Squaxin Island",
         position = "bottom",
         logger_id = NA_character_,
         logger_type = "water level",
         issue_flag = NA_character_,
         comments = NA_character_) 

# select cols to match data
sqx_fix <- sqx_fix |>
  select(c("site", "position", "datetime", "logger_id", "logger_type",
           "issue_flag", "comments", "wl_temp_c", "abs_pres_kpa"))

# combine
pres_sqx_filled <- rbind(pres_sqx, sqx_fix) |>
  arrange(datetime) |>
  filter(!is.na(abs_pres_kpa))

# visual check
ggplot(pres_sqx_filled) +
  geom_point(aes(x = datetime, y = abs_pres_kpa))
```

### Combine all pressure data

```{r}
# bind pres data ----
pressure <- bind_rows(pressure_wp, pres_ed, pres_sqx_filled) |>
  select(site, position, datetime, wl_temp_c, abs_pres_kpa,
         comments) |>
  rename("temp_c" = "wl_temp_c",
         "absolute_pressure_kpa" = "abs_pres_kpa")

# check combine
ggplot(pressure) +
  geom_point(aes(x = datetime, y = absolute_pressure_kpa, color = site),
             alpha = 0.5, size = 0.2)

# check ranges
pressure_check <- pressure |>
  group_by(site) |>
  reframe(range = range(datetime))
```
```{r}
# save file
# write_csv(pressure,
#           here("data", "processed", "pressure.csv"))
```
