---
title: "prep_for_dnr"
format: html
---

Script to prepare data for sharing with DNR for sensor comparisons.

**Think of including:**

-   temp
-   salinity
-   light
-   pressure

all from the surface and benthos when available.

**Share data for:**

-   Wing Pt, 6-14-24 to 2-26-25

    -   Temp: surface and bottom ready to go!

-   Edmonds, 6-18-2024 to 2-18-25

     -   Temp: surface and bottom ready to go!

-   Squaxin, 9-25-24 to 8-21-25

-   Squaxin, 11-15-25 to 3-9-26+

**Prep work:**

-   Confirm that issue flags are matching correctly to time frames
    -   Most recent full data update (4/1/2026) issue flag matching **not** working.
    -   Need to:
        1.  update pipeline to accommodate new (improved) metadata format and
        2.  run pipeline (passive, but time consuming)
    -   Note: sites managed by partners still using old (wide) metadata format
    -   **Decide:** Manually check issues for requested data and update pipeline later? Or use as excuse to work on pipeline now, and further delay data sharing?
-   Remove "bad" data flags
-   Have all PAR been calibrated for these deployments?
-   Do we share conductivity, despite knowing that values are off?
-   What associated metadata do I need to write?

## Setup

```{r}
# load libraries ----
library(tidyverse)
library(here)

# load data ----
# note: using data updated on 4/1/2026
temp <- readRDS(here("data", "logger_data_temp.rds"))
salinity <- readRDS(here("data", "logger_data_con.rds"))
light <- readRDS(here("data", "logger_data_par.rds"))
pressure <- readRDS(here("data", "logger_data_wl.rds"))
ph <- readRDS(here("data", "logger_data_ph.rds")) # best bottom temp data comes from pH sensor
metadata <- read_csv(here("data", "metadata.csv")) # metadata from 7/27/2026
```

## Temp

#### Wing Point

6-14-24 to 2-26-25

**Surface**

```{r}
# Filter to site & date range ----
wing_pt_temp_surface <- temp |>
  filter(site == "Wing Point",
         between(datetime, ymd_hms("2024-06-14 00:00:00"), ymd_hms("2025-02-26 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(wing_pt_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```

**Bottom**

```{r}
# Filter to site & date range ----
wing_pt_temp_bottom <- ph |>
  filter(site == "Wing Point",
         between(datetime, ymd_hms("2024-06-14 00:00:00"), ymd_hms("2025-02-26 23:59:59")),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# check filter
ggplot(wing_pt_temp_bottom) +
  geom_point(aes(x = datetime, y = temp_c))
```

```{r}
# combine surface and bottom at wing pt
wing_pt_temp <- bind_rows(wing_pt_temp_surface, wing_pt_temp_bottom)

# check combine
ggplot(wing_pt_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Check issue flags

```{r}
# function to create issue flag plots ----
issue_plot_builder <- function(data, site_name, pos, sensor_col, y_label, title_sensor) {
  
  # Filter to this site/position
  plot_data <- data |>
    filter(site == site_name,
           position == pos)

  
  # Build flagged periods
  issue_periods <- plot_data |>
    filter(!is.na(issue_flag)) |>
    arrange(datetime) |>
    mutate(
      time_gap = as.numeric(difftime(datetime, lag(datetime), units = "hours")),
      new_group = is.na(time_gap) | issue_flag != lag(issue_flag, default = "") | time_gap > 1,
      group_id = cumsum(new_group)
    ) |>
    group_by(site, position, issue_flag, group_id) |>
    summarise(start = min(datetime),
              end = max(datetime),
              .groups = "drop")
  
  # Plot
  ggplot(plot_data |> 
           mutate(year = year(datetime)),
         aes(x = datetime, y = .data[[sensor_col]])) +
    geom_rect(data = issue_periods |> 
                mutate(year = year(start)),
              aes(xmin = start, xmax = end, ymin = -Inf, ymax = Inf, fill = issue_flag),
              inherit.aes = FALSE, alpha = 0.2) +
    geom_point(alpha = 0.3, size = 0.8) +
    labs(title = paste0(site_name, ", ", str_to_title(pos), ", ", title_sensor, " (Raw)"),
         subtitle = "Data issues for deployments highlighted behind points",
         y = y_label,
         fill = "Issue Flag") +
    facet_wrap(~ year, 
               scales = "free_x", 
               ncol = 1) +
    theme_minimal(base_size = 12) +
    theme(plot.title.position = "plot")
}
```

```{r}
# check for issues
issue_plot_builder(wing_pt_temp, "Wing Point", "surface", "temp_c", "C", "temp")
```

```{r}
# check for issues
issue_plot_builder(wing_pt_temp, "Wing Point", "bottom", "temp_c", "C", "temp")
```

**Wing Point temp data good to go**

Manually check issues against metadata

```{r}
wp_meta_temp_surface <- metadata |>
  filter(site == "Wing Point",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-06-13"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags for surface
```
```{r}
wp_meta_temp_bottom <- metadata |>
  filter(site == "Wing Point",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2024-06-13"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags for bottom
```


#### Edmonds

6-18-2024 to 2-18-25

**Surface**

```{r}
# Filter to site & date range ----
edmonds_temp_surface <- temp |>
  filter(site == "Edmonds",
         between(datetime, ymd_hms("2024-06-18 00:00:00"), ymd_hms("2025-02-18 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(edmonds_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```

**Bottom**

```{r}
# Filter to site & date range ----
edmonds_temp_bottom <- ph |>
  filter(site == "Edmonds",
         between(datetime, ymd_hms("2024-06-18 00:00:00"), 
                 ymd_hms("2025-02-18 23:59:59")),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# check filter
ggplot(edmonds_temp_bottom) +
  geom_point(aes(x = datetime, y = temp_c))
```

```{r}
# combine surface and bottom
edmonds_temp <- bind_rows(edmonds_temp_surface, edmonds_temp_bottom)

# check combine
ggplot(edmonds_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Check issue flags

```{r}
# surface issue check
issue_plot_builder(edmonds_temp, "Edmonds", "surface", "temp_c", "C", "temp")
```

Automatic issue flag not working on most recent data update. 

Manually check issues against metadata

```{r}
ed_meta_temp_surface <- metadata |>
  filter(site == "Edmonds",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-06-10"),
         in_water_date <= as.Date("2025-02-19"))

# 1 issue flag: failure to offload. was later offloaded at office, so no action needed.
```

```{r}
ed_meta_temp_bottom <- metadata |>
  filter(site == "Edmonds",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2024-06-10"),
         in_water_date <= as.Date("2025-02-19"))

# no issue flags
```

**Edmonds temp data good to go for surface and bottom**

#### Squaxin

9-25-24 to 8-21-25;

11-15-25 to 3-9-26+

**Surface**

Range 1:
```{r}
# Filter to site & date range ----
squaxin_temp_surface <- temp |>
  filter(site == "Squaxin Island",
         between(datetime, ymd_hms("2024-09-25 00:00:00"), ymd_hms("2025-08-21 23:59:59"))) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(squaxin_temp_surface) +
  geom_point(aes(x = datetime, y = temp_c))
```

Range 2:
```{r}
# Filter to site & date range ----
squaxin_temp_surface2 <- temp |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2025-11-15 00:00:00")) |>
  rename("temp_c" = "tidbit_temp_c")

# check filter
ggplot(squaxin_temp_surface2) +
  geom_point(aes(x = datetime, y = temp_c))
```


**Bottom**

```{r}
# Filter to site & date range ----
squaxin_temp_bottom2 <- ph |>
  filter(site == "Squaxin Island",
         datetime >= ymd_hms("2025-11-15 00:00:00"),
         position == "bottom") |>
  rename("temp_c" = "ph_temp_c")

# check filter
ggplot(squaxin_temp_bottom2) +
  geom_point(aes(x = datetime, y = temp_c))
```

```{r}
# combine surface and bottom
squaxin_temp <- bind_rows(squaxin_temp_surface, squaxin_temp_surface2,
                          squaxin_temp_bottom, squaxin_temp_bottom2)

# check combine
ggplot(squaxin_temp) +
  geom_point(aes(x = datetime, y = temp_c)) +
  facet_wrap(~position, ncol = 1)
```

Manually check issues against metadata

```{r}
sqx_meta_temp_surface <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "temperature",
         in_water_date >= as.Date("2024-09-20"),
         in_water_date <= as.Date("2025-08-22"))

# No issue flags

sqx_meta_temp_surface2 <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "temperature",
         in_water_date >= as.Date("2025-11-10"))

# No issue flags
```

```{r}
sqx_meta_temp_bottom <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2024-09-20"),
         in_water_date <= as.Date("2025-08-22"))

# No issue flags

sqx_meta_temp_bottom2 <- metadata |>
  filter(site == "Squaxin Island",
         logger_type == "ph",
         position == "bottom",
         in_water_date >= as.Date("2025-11-10"))

# No issue flags
```

Squaxin temp data good to go. 

### Combine all temp data

```{r}
# bind temp data ----
temperature <- bind_rows(wing_pt_temp, edmonds_temp, squaxin_temp) |>
  select(site, position, datetime, temp_c, comments)

# check combine
ggplot(temperature) +
  geom_point(aes(x = datetime, y = temp_c, color = site),
             alpha = 0.5, size = 0.2) +
  facet_wrap(~position)

# check ranges
temp_check <- temperature |>
  group_by(site) |>
  reframe(range = range(datetime))
```

```{r}
# export temp data
# write_csv(temperature, here("data", "processed", "temperature.csv"))
```


------------------------------------------------------------------------

## Salinity

#### Wing Point

#### Edmonds

#### Squaxin

------------------------------------------------------------------------

## Light

Light is only collected at the benthos.

#### Wing Point

6-14-24 to 2-26-25

```{r}
# Filter to site & date range ----
wing_pt_light <- light |>
  filter(site == "Wing Point",
         between(datetime, ymd_hms("2024-06-14 00:00:00"), ymd_hms("2025-02-26 23:59:59")))

# check filter
ggplot(wing_pt_light) +
  geom_point(aes(x = datetime, y = calibrated_integrating_light))
```


#### Edmonds

#### Squaxin

------------------------------------------------------------------------

## Pressure

#### Wing Point

#### Edmonds

#### Squaxin
